Msc Thesis Figures

### 2020-07-23 Rmd/msc_thesis_figures.Rmd
updates

```{r BAU, message=FALSE, warning=FALSE}
sce_39 <- stack(lapply((list.files("test/july/sce_39_BAU/", full.names = T)), raster))
stratum <- raster("data/stsim/aggregated/primary_stratum_mont_or_not_or_PA.tif")
the_names <- names(sce_39)
sce_39[stratum == 0] <- NA
names(sce_39) <- the_names

ts_2_39 <- sce_39[[which(stringr::str_detect(names(sce_39), "ts2"))]]
ts_11_39 <- sce_39[[which(stringr::str_detect(names(sce_39), "ts11"))]]

two_stack_39 <-  stack(sce_39$sc.it5.ts2, sce_39$sc.it5.ts11)
names(two_stack_39) <- c("2010", "2100")
# plot(trim(two_stack))

ts_2_freq_39 <- freq(ts_2_39, useNA="no")
ts_11_freq_39 <- freq(ts_11_39, useNA="no")

full_df_2_39 <- data.frame()
for (x in 1:length(ts_2_freq_39)){
  temp_df_39 <- ts_2_freq_39[[x]] %>% 
    as.data.frame() %>% 
    mutate(iteration = paste0("iter_", x)) %>% 
    mutate(timestep = 2010)
  full_df_2_39 <- bind_rows(full_df_2_39, temp_df_39)
}

full_df_11_39 <- data.frame()
for (x in 1:length(ts_11_freq_39)){
  temp_df_39 <- ts_11_freq_39[[x]] %>% 
    as.data.frame() %>% 
    mutate(iteration = paste0("iter_", x)) %>% 
    mutate(timestep = 2100)
  full_df_11_39 <- bind_rows(full_df_11_39, temp_df_39)
}

full_df_39 <- bind_rows(full_df_2_39, full_df_11_39)

mean_df_39 <- full_df_39 %>% 
  group_by(timestep, value) %>% 
  summarise(mean_count = mean(count)) %>% ungroup()

sd_df_39 <- full_df_39 %>% 
  group_by(timestep, value) %>% 
  summarise(sd_count = sd(count)) %>% ungroup()

final_df_39 <- left_join(mean_df_39, sd_df_39,  by = c("timestep", "value")) %>% 
  left_join(classes_unique, 
            by=c("value"="new_code")) %>% 
  filter(!(value %in% c(4,5,6))) %>%
  mutate(area = mean_count*((90*90)/10000))

@@

```{r reforestation, message=FALSE, warning=FALSE}
sce_42 <- stack(lapply((list.files("test/july/sce_42_Ref/", full.names = T)), raster))
stratum <- raster("data/stsim/aggregated/primary_stratum_mont_or_not_or_PA.tif")
the_names <- names(sce_42)
sce_42[stratum == 0] <- NA
names(sce_42) <- the_names

ts_2_42 <- sce_42[[which(stringr::str_detect(names(sce_42), "ts2"))]]
ts_11_42 <- sce_42[[which(stringr::str_detect(names(sce_42), "ts11"))]]

two_stack_42 <-  stack(sce_42$sc.it5.ts2, sce_42$sc.it5.ts11)
names(two_stack_42) <- c("2010", "2100")
# plot(trim(two_stack))

ts_2_freq_42 <- freq(ts_2_42, useNA="no")
ts_11_freq_42 <- freq(ts_11_42, useNA="no")

full_df_2_42 <- data.frame()
for (x in 1:length(ts_2_freq_42)){
  temp_df_42 <- ts_2_freq_42[[x]] %>% 
    as.data.frame() %>% 
    mutate(iteration = paste0("iter_", x)) %>% 
    mutate(timestep = 2010)
  full_df_2_42 <- bind_rows(full_df_2_42, temp_df_42)
}

full_df_11_42 <- data.frame()
for (x in 1:length(ts_11_freq_42)){
  temp_df_42 <- ts_11_freq_42[[x]] %>% 
    as.data.frame() %>% 
    mutate(iteration = paste0("iter_", x)) %>% 
    mutate(timestep = 2100)
  full_df_11_42 <- bind_rows(full_df_11_42, temp_df_42)
}

full_df_42 <- bind_rows(full_df_2_42, full_df_11_42)

mean_df_42 <- full_df_42 %>% 
  group_by(timestep, value) %>% 
  summarise(mean_count = mean(count)) %>% ungroup()

sd_df_42 <- full_df_42 %>% 
  group_by(timestep, value) %>% 
  summarise(sd_count = sd(count)) %>% ungroup()

final_df_42 <- left_join(mean_df_42, sd_df_42,  by = c("timestep", "value")) %>% 
  left_join(classes_unique, 
            by=c("value"="new_code")) %>% 
  filter(!(value %in% c(4,5,6))) %>%
  mutate(area = mean_count*((90*90)/10000))

@@

>>>>

```{r BAU, message=FALSE, warning=FALSE}
# draw_scenario(39)
final_df_39 <- draw_scenario(39, return_df = T)

@@

```{r reforestation, message=FALSE, warning=FALSE}
# draw_scenario(42)
final_df_42 <- draw_scenario(42, return_df = T)

@@

```{r BAU, message=FALSE, warning=FALSE}
# draw_scenario(42) ...

all_chap2 <- draw_scenario(42, return_df = T) %>% 
  bind_rows(draw_scenario(45, return_df = T)) %>% 
  bind_rows(draw_scenario(48, return_df = T)) %>% 
  bind_rows(draw_scenario(51, return_df = T))

#forest <-

bar_chap2 <- all_chap2 %>% 
  mutate(value = ifelse(.$value>10, 10, .$value)) %>%
  mutate(new_class = ifelse(.$value == 10, "forest", .$new_class)) %>% 
  group_by(new_class, timestep, scenario, value) %>% 
  summarise(area = sum(area)) %>% ungroup() %>% 
  filter(value %in% c(1,2,10)) %>% 
  left_join(results_clean, by = c("scenario"="scenarioId")) %>% 
  mutate(value = as.factor(value), timestep = as.factor(timestep)) %>% 
  ggplot(aes(fill=timestep, y=area, x=new_class)) + 
  geom_bar(position="dodge", stat="identity") +
  facet_wrap(~name, labeller = label_wrap_gen(width = 30)) +
  theme(legend.position = c(0.85, 0.7)) +
  labs(x = "Land use Class", 
       y = "Mean Area (hectare)", 
       fill = "Year") +
  NULL
bar_chap2
ggsave("../msc-thesis-mcgill/figures/bar_chap2.png", bar_chap2, width = 15, height = 20)
```
